---
title: "P8105_hw6_yx2510"
author: "Yi Xiao"
date: "20/11/2018"
output: html_document
---

```{r}
library(tidyverse)
library(stringr)
library(broom)
library(leaps)
library(modelr)
library(mgcv)
```

## Problem one:
1. read and tidy the data:
```{r message = FALSE}
homicide_data = read_csv("./data/homicide-data.csv") %>%
        janitor::clean_names() %>%
        unite(col = "city_state", city:state, sep = ", ", remove = FALSE) %>%
        mutate(solved = ifelse(disposition == "Closed by arrest", 1, 0),
               victim_race = ifelse(victim_race == "White", "white", "non_white"),
               victim_race = fct_relevel(victim_race, "white", "non_white"),
               victim_age = as.numeric(victim_age)) %>%
        filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
```
2. fit a logistic regression with resolved
```{r}
baltimore_data = homicide_data %>%
        filter(city_state == "Baltimore, MD")
baltimore_model = baltimore_data %>% 
        glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

baltimore_model %>% 
  broom::tidy() %>%  # give log odds ratio
  mutate(OR = exp(estimate), # transform back
         lower_bound = exp(estimate - std.error*1.96),
         upper_bound = exp(estimate + std.error*1.96)) %>%
  filter(term == "victim_racenon-White") %>% 
  select(term, log_OR = estimate, OR, lower_bound, upper_bound, p.value) %>% 
  rename("odds_ratio" = OR, "log_odds_ratio" = log_OR) 
```

Comment: the odds ratio estimate for victom_race (non_white) is 0.441 with 95% confidence interval being 0.313 to 0.62. This suggested that the odds of solving the non-white-related cases is 0.441 as that of the-white-invloved cases. 

3. Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims.

```{r}
homicide_nest = homicide_data %>% 
  group_by(city_state) %>% 
  nest()

homicide_nest %>% 
  mutate(models = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenon_white") %>% 
  mutate(OR = exp(estimate),
         lower_bound = exp(estimate - std.error*1.96),
         upper_bound = exp(estimate + std.error*1.96)) %>%
  select(city_state, term, OR, lower_bound, upper_bound) %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + geom_point() + 
  geom_errorbar(mapping = aes(ymin = lower_bound, ymax = upper_bound)) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 90, size = 7)) +
 coord_flip() + 
  labs(y = "Odds ratio", 
       x = "City, State")
```

### Problem two:
1. Load and clean the data for regression analys
```{r}
birth_data = read_csv("./data/birthweight.csv") %>%
   janitor::clean_names()
   
birth_tidy = birth_data %>%
    mutate(babysex = as.factor(babysex),
           frace = as.factor(frace),
           malform = as.factor(malform),
           mrace = as.factor(mrace),
            bwt = bwt*0.0022
           ) 
```

